Bandit Multiclass Classification

### 2018-08-15 main.tex
add a last paragraph to Selectron section
Type-2 margin

\section{Logarithmic Regret for Strongly Convex and Smooth Losses}
\subsection{Gradient descent}
In some previous works (we will visit them in the next subsection), it is assumed that the labels are generated with the following process: 
\begin{align}
    p(y|x) = \nabla_y\Phi(W^*x), 
\end{align}
which some $\Phi: \mathbb{R}^K \rightarrow \mathbb{R}$.
The margin assumption is defined as 
\begin{align}
    p(y_t|x_t) - \max_{y\neq y_t}p(y|x_t) \geq \Delta, \forall t.  \label{eqn:new margin}
\end{align}
This margin assumption is a special case of the Tsybakov condition investigated in ~\cite{agarwal2013selective}. 
Defining $\hat{y}_t = \argmax_y \nabla\Phi(W_tx_t)$ and $y^*_t = \argmax_y \nabla\Phi(W^*x_t) $ The regret is defined as
\begin{align}
    \Reg_T &= \sum_{t=1}^T \E\left[ \one[\hat{y}_t\neq y_t] - \one[y_t^*\neq y_t]\right] \tag{the $\E[\cdot]$ is conditioned on all history before time $t$ and the randomness is from $y_t$} \\
    &= \sum_{t=1}^T \sum_{i=1}^K \left(\one[\hat{y}_t\neq i] - \one[y^*_t\neq i]\right)\nabla_i\Phi(W^*x_t). \label{eqn:new regret}
\end{align}

@@

\begin{theorem}
\label{lemma:new main}
The selective sampling algorithm achieves
\begin{align*}
    \Reg_T\leq \tilde{O}\left( \frac{\gamma_u^2}{\gamma_\ell^2}\frac{K^2d}{\Delta^2} \right). 
\end{align*}
\end{theorem}

@@

\begin{lemma}
\label{lem: xbounded}
If $\|x_t\|_{M_t^{-1}}\leq \epsilon = \Delta/(2\gamma_u C')$, then $\hat{y}_t=y^*_t$. 
\end{lemma}
\begin{proof}
\begin{align*}
\nb \Phi_{y_t^*}(W^*x_t) - \nb\Phi_{\hat{y}_t}(W^*x_t) 
 &\leq \nb \Phi_{y_t^*}(W^*x_t) -    \nb\Phi_{\hat{y}_t}(W^*x_t) 
 - \nb \Phi_{y_t^*}(W_tx_t) + \nb \Phi_{\hat{y}_t}(W_tx_t) \\
 & \leq 2\gamma_u \|W^*x_t-W_tx_t\|_2 \\
 & \leq 2\gamma_u \|W^*-W_t\|_{M_t}\|x_2\|_{M_t^{-1}} \\
 & \leq \Delta. \tag{by Lemma~\ref{lem:decreasing error}}
\end{align*}
By the margin assumption \eqref{eqn:new margin}, $\hat{y}_t = y_t^*$. 
\end{proof}

@@

\subsection{Revisiting the stochastic assumptions made in \cite{crammer2013multiclass} and \cite{agarwal2013selective}}
In \cite{crammer2013multiclass} and \cite{agarwal2013selective}, the feature vectors $x_t$'s are adversarially picked, while $y_t$ is generated based on some conditional distribution based on $x_t$. For example, in \cite{crammer2013multiclass}, the label is generated by
\begin{align}
    p(y_t = i | x_t) = \frac{\alpha + (W^*x_t)_i}{\alpha+1}, \label{eqn:confidit assumption}
\end{align}
where $W^* \in \Omega_t \triangleq \{W\in \mathbb{R}^{K\times d}: \sum_{i=1}^K (Wx_t)_i = \alpha+1-K\alpha \text{\ and\ } -\alpha \leq (Wx_t)_i\}$; a valid $\Phi$ that satisfies \eqref{eqn:new margin} is 
\begin{align}
    \Phi(u) = \frac{1}{2(\alpha+1)}\|u\|_2^2 + \frac{\alpha}{\alpha+1}\sum_{i=1}^K u_i. 
\end{align}
in \cite{agarwal2013selective}, the labels are generated by 
\begin{align}
    p(y_t = i | x_t) = \frac{\exp((W^*x_t)_i)}{\sum_{j=1}^K \exp((W^*x_t)_j) },
\end{align}
where $W^* \in \Omega \triangleq \{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W\|_2 \leq D \}$, and $\Phi$ can be chosen as
\begin{align}
    \Phi(u) = \log\left(\sum_{i=1}^K \exp(u_i) \right). 
\end{align}

>>>>

\section{Logarithmic Regret for Strongly Convex and Smooth Losses}
\subsection{Gradient descent}
In some previous works (we will visit them in the next subsection), it is assumed that the labels are generated with the following process: 
\begin{align}
    p(y|x) = \nabla_y\Phi(W^*x), 
\end{align}
with some $\Phi: \mathbb{R}^K \rightarrow \mathbb{R}$. This is a \textit{generalized linear model}.  
The margin assumption is defined as 
\begin{align}
    p(y_t|x_t) - \max_{y\neq y_t}p(y|x_t) \geq \Delta, \forall t.  \label{eqn:new margin}
\end{align}

{\color{blue} Type 2 margin assumption: }\\
{\color{blue} 
\begin{align}
    (W^*x_t)_{y_t} - \max_{y\neq y_t}(W^*x_t)_{y} \geq \Delta. 
\end{align}

}

This margin assumption is a special case of the Tsybakov condition investigated in ~\cite{agarwal2013selective}. 
Defining $\hat{y}_t = \argmax_y \nabla\Phi(W_tx_t)$ and $y^*_t = \argmax_y \nabla\Phi(W^*x_t) $ The regret is defined as
\begin{align}
    \Reg_T &= \sum_{t=1}^T \E\left[ \one[\hat{y}_t\neq y_t] - \one[y_t^*\neq y_t]\right] \tag{the $\E[\cdot]$ is conditioned on all history before time $t$ and the randomness is from $y_t$} \\
    &= \sum_{t=1}^T \sum_{i=1}^K \left(\one[\hat{y}_t\neq i] - \one[y^*_t\neq i]\right)\nabla_i\Phi(W^*x_t). \label{eqn:new regret}
\end{align}

@@

\begin{theorem}
\label{lemma:new main}
The selective sampling algorithm achieves
\begin{align*}
    \Reg_T\leq \tilde{O}\left( \frac{\gamma_u^2}{\gamma_\ell^2}\frac{K^2d}{\Delta^2} \right). 
\end{align*}
{\color{blue} For Type 2 margin assumption, the bound is
\begin{align*}
    \Reg_T \leq \tilde{O}\left(\frac{1}{\gamma_\ell^2}\frac{K^2d}{\Delta^2}\right).
\end{align*}

}
\end{theorem}

@@

\begin{lemma}
\label{lem: xbounded}
If $\|x_t\|_{M_t^{-1}}\leq \epsilon = \Delta/(2\gamma_u C')$, then $\hat{y}_t=y^*_t$. {\color{blue}(For Type 2 margin assumption, we set $\epsilon=\Delta/2C'$)}
\end{lemma}
\begin{proof}
\begin{align*}
\nb \Phi_{y_t^*}(W^*x_t) - \nb\Phi_{\hat{y}_t}(W^*x_t) 
 &\leq \nb \Phi_{y_t^*}(W^*x_t) -    \nb\Phi_{\hat{y}_t}(W^*x_t) 
 - \nb \Phi_{y_t^*}(W_tx_t) + \nb \Phi_{\hat{y}_t}(W_tx_t) \\
 & \leq 2\gamma_u \|W^*x_t-W_tx_t\|_2 \\
 & \leq 2\gamma_u \|W^*-W_t\|_{M_t}\|x_2\|_{M_t^{-1}} \\
 & \leq \Delta. \tag{by Lemma~\ref{lem:decreasing error}}
\end{align*}
By the margin assumption \eqref{eqn:new margin}, $\hat{y}_t = y_t^*$. 
\end{proof}

{\color{blue} For Type 2 margin assumption, the proof is following:  
\begin{proof}
\begin{align*}
    (W^*x_t)_{y_t^*} - (W^*x_t)_{\hat{y}_t} &\leq (W^*x_t)_{y_t^*} - (W^*x_t)_{\hat{y}_t} - (W_tx_t)_{y_t^*} + (W_tx_t)_{\hat{y}_t} \\
    &\leq 2\|W^*x_t-W_tx_t\|_2\\
    & \leq 2 \|W^*-W_t\|_{M_t}\|x_2\|_{M_t^{-1}} \\
    & \leq \Delta.
\end{align*}
\end{proof}
}

@@

\subsection{Revisiting the stochastic assumptions made in \cite{crammer2013multiclass} and \cite{agarwal2013selective}}
In \cite{crammer2013multiclass} and \cite{agarwal2013selective}, the feature vectors $x_t$'s are adversarially picked, while $y_t$ is generated based on some conditional distribution based on $x_t$. For example, in \cite{crammer2013multiclass}, the label is generated by
\begin{align}
    p(y_t = i | x_t) = \frac{\alpha + (W^*x_t)_i}{\alpha+1}, \label{eqn:confidit assumption}
\end{align}
where $W^* \in \Omega_t \triangleq \{W\in \mathbb{R}^{K\times d}: \sum_{i=1}^K (Wx_t)_i = \alpha+1-K\alpha \text{\ and\ } -\alpha \leq (Wx_t)_i\}$; a valid $\Phi$ that satisfies \eqref{eqn:new margin} is 
\begin{align}
    \Phi(u) = \frac{1}{2(\alpha+1)}\|u\|_2^2 + \frac{\alpha}{\alpha+1}\sum_{i=1}^K u_i. 
\end{align}
in \cite{agarwal2013selective}, the labels are generated by 
\begin{align}
    p(y_t = i | x_t) = \frac{\exp(\beta(W^*x_t)_i)}{\sum_{j=1}^K \exp(\beta(W^*x_t)_j) },
\end{align}
where $W^* \in \Omega \triangleq \{W\in \mathbb{R}^{K\times d}: \|\e_i^\top W\|_2 \leq 1 \}$, and $\Phi$ can be chosen as
\begin{align}
    \Phi(u) = \frac{1}{\beta}\log\left(\sum_{i=1}^K \exp(\beta u_i) \right). 
\end{align}

If we want, we can also cast our original linear separability to this framework: 
\begin{align}
    p(y_t=i|x_t) = \one\left[(W^*x_t)_i \geq (W^*x_t)_j, \forall j\neq i\right]. 
\end{align}
A natural definition of $\Phi$ is
\begin{align}
    \Phi(u) = \max_i u_i. 
\end{align}
